### 2022-12-05 paper1.tex
table formatting

\end{knitrout}
\caption{Relative effect size $d$ versus original $p$-value $p_o$. Black
  indicates that replication success was achieved at the golden level while grey
  indicates that it was not. The diamonds mark studies where the replication
  success approach (at the golden level) and the two-trials rule disagree. The
  dashed black line indicates the limiting relative effect size at the golden
  level with $\alpha = 0.025$. }
\label{fig2:fig6}
\end{figure}

Figure~\ref{fig2:fig6} displays the relative effect size $d$ versus the original
$p$-value $p_o$ for each study pair and stratified by project. Note that one
study pair from the Philosophy project is not shown due to extremely small
original $p$-value and another study pair from the Psychology project is not
shown due to a very large relative effect size. We can see that for most of the
study pairs, the replication success approach and the two-trials rule lead to
the same conclusion, only six replications show conflicting results. They are
highlighted with diamonds in Figure~\ref{fig2:fig6} and their characteristics are
summarised in Table~\ref{tbl:discrep}.
\begin{table}[!ht]
    \centering
  \caption{Characteristics of studies for which the replication success approach
    (at the golden level) and the two-trials rule disagree (at one-sided
    $\alpha = 0.025$). Shown are relative sample size $c$, relative effect size
    $d$, original, replication and recalibrated sceptical $p$-value $p_o$, $p_r$
    and $\tilde{p}_S$.}
  \label{tbl:discrep}
\resizebox{\textwidth}{!} {
% latex table generated in R 4.0.5 by xtable 1.8-4 package
% Fri Nov 25 12:12:30 2022
\begin{tabular}{lllllll}
  \toprule
Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_S$ \\
  \midrule
\citet{Schmidt2008} & Psychology & 2.58 & 1.28 & \textbf{0.028} & \textcolor{black}{< 0.0001} & \textcolor{black}{0.024} \\
  \citet{Oberauer2008} & Psychology & 0.60 & 0.67 & \textcolor{black}{0.0003} & \textbf{0.035} & \textcolor{black}{0.017} \\
  \citet{Payne2008} & Psychology & 2.65 & 0.41 & \textcolor{black}{0.001} & \textcolor{black}{0.023} & \textbf{0.031} \\
  \citet{Balafoutas2012} & Social Sciences & 3.48 & 0.52 & \textcolor{black}{0.009} & \textcolor{black}{0.011} & \textbf{0.04} \\
  \citet{Pyc2010} & Social Sciences & 9.18 & 0.38 & \textcolor{black}{0.011} & \textcolor{black}{0.004} & \textbf{0.061} \\
  \citet{Nichols2006} & Experimental Philosophy & 9.40 & 0.49 & \textcolor{black}{0.015} & \textcolor{black}{0.0006} & \textbf{0.049} \\
   \bottomrule
\end{tabular}%
}
\end{table}
Two studies from the Psychology project show replication success but fail the
two-trials rule. These studies show $p$-values that are slightly above the
significance threshold in either original or replication study, but do not
exhibit much shrinkage; in the replication of \citet{Oberauer2008}, the
replication $p$-value was $p_r = 0.035$, a little too large to pass the
two-trials rule. However, as the replication effect estimate shrunk only about
$30$\% compared to the original one, replication success is still achieved.
Conversely, the original $p$-value $p_o = 0.028$ in \citet{Schmidt2008} was just
above the significance level, yet the replication led to a highly significant
result $p_r < 0.0001$ with the effect estimate being even $30$\% larger than the
original counterpart, which therefore also resulted in replication success.

@@

This analysis was based on the default choice $\dinfty=1$ at $\alpha=0.025$ for
the golden level as described in Section \ref{sec2:goldenthresh}. We may also
choose a different value for the limiting relative effect size $\dinfty$ at
$\alpha=0.025$ which then corresponds to $\dinfty=1$ at a different level
$\alpha'$ as given in \eqref{eq2:alphaPrime}. Figure \ref{fig2:fig7} compares the
proportion of successful replications with the replication success approach for
$\dinfty \in (0.5, 1.1)$ with the two-trials rule at the
corresponding levels
$\alpha' \in (0.06, 0.022)$ for
all four replication projects. We can see that the two proportions agree fairly
well for all values of $\alpha'$ considered. The number of discrepant studies in
each project varies between 0 and 3. Only in the Psychology project there are
some studies which are successful with the replication success approach but not
the two-trials rule and some studies successful with the two-trials rule but not
the replication success approach. The proportion of studies where both methods
are successful (also shown in Figure \ref{fig2:fig7}) is then smaller than the
proportion of successful replications with either one of the two methods. The
three discrepant studies from the Psychology project listed in the top three
rows of Table~\ref{tbl:discrep} are an example of this particular feature.

@@

\end{knitrout}
\caption{Proportion of successful replications as a function of the limiting
  relative effect size $\dinfty$ at $\alpha = 0.025$. The upper axis gives the
  equivalent level $\alpha'$ where the corresponding limiting relative effect
  size is 1. The replication success (RS) approach is compared with the
  two-trials rule (2TR).}
\label{fig2:fig7}
\end{figure}

\section{Discussion}\label{sec2:discussion}
In this paper, we have expanded on the replication success approach introduced
in \citet{Held2020} and demonstrated its advantages over alternative methods
such as the two-trials rule. In particular, the method provides an attractive
compromise between hypothesis testing and estimation,
as it penalizes
shrinkage of the replication effect estimate compared to the original one,
while ensuring that both are statistically significant to some extent.
%% For instance, the method will indicate only a low degree of replication success when
%% the replication study shows a much smaller but statistically significant
%% effect estimate, whereas it can still indicate some degree of
%% success when either original or replication $p$-value are slightly above the
%% significance level. %% , provided their effect estimates are compatible.

@@

Throughout the paper we have assumed that the relative sample size is fixed in
advance. In practice the sample size of the replication study is often chosen
based on the result of the original study \citep{Anderson2017}. Power
calculations as shown in Figure \ref{fig2:fig3} can then be inverted to determine
the appropriate sample size of the replication study. We can also invert
equation \eqref{eq2:res} to obtain the required replication sample size based on
the specification of the minimum relative effect size $\dmin$ to achieve
replication success. This novel way of calculating the sample size requires the
specification of the minimum relative effect size which can still be considered
as acceptable. Sample size calculations based on the two-trials rule can also be
formulated in terms of the minimum relative effect size by inverting equation
\eqref{eq2:dSig}. We will report on a detailed comparison of the different
approaches in future work.

>>>>

\end{knitrout}
\caption{Relative effect size $d$ versus original $p$-value $p_o$. Black
  indicates that replication success was achieved at the golden level while grey
  indicates that it was not. The diamonds mark studies where the replication
  success approach (at the golden level) and the two-trials rule disagree. The
  dashed black line indicates the limiting relative effect size at the golden
  level with $\alpha = 0.025$. }
\label{fig1:fig6}
\end{figure}

Figure~\ref{fig1:fig6} displays the relative effect size $d$ versus the original
$p$-value $p_o$ for each study pair and stratified by project. Note that one
study pair from the Philosophy project is not shown due to extremely small
original $p$-value and another study pair from the Psychology project is not
shown due to a very large relative effect size. We can see that for most of the
study pairs, the replication success approach and the two-trials rule lead to
the same conclusion, only six replications show conflicting results. They are
highlighted with diamonds in Figure~\ref{fig1:fig6} and their characteristics are
summarised in Table~\ref{tbl:discrep}.
\begin{table}[!ht]
    \centering
  \caption{Characteristics of studies for which the replication success approach
    (at the golden level) and the two-trials rule disagree (at one-sided
    $\alpha = 0.025$). Shown are relative sample size $c$, relative effect size
    $d$, original, replication and recalibrated sceptical $p$-value $p_o$, $p_r$
    and $\tilde{p}_S$.}
  \label{tbl:discrep}
\resizebox{\textwidth}{!} {
% latex table generated in R 4.0.5 by xtable 1.8-4 package
% Fri Nov 25 12:12:30 2022
\begin{tabular}{lllllll}
  \toprule
Study & Project & $c$ & $d$ & $p_o$ & $p_r$ & $\tilde{p}_S$ \\
  \midrule
\citet{Schmidt2008} & Psychology & 2.58 & 1.28 & \textbf{0.028} & \textcolor{black}{< 0.0001} & \textcolor{black}{0.024} \\
  \citet{Oberauer2008} & Psychology & 0.60 & 0.67 & \textcolor{black}{0.0003} & \textbf{0.035} & \textcolor{black}{0.017} \\
  \citet{Payne2008} & Psychology & 2.65 & 0.41 & \textcolor{black}{0.001} & \textcolor{black}{0.023} & \textbf{0.031} \\
  \citet{Balafoutas2012} & Social Sciences & 3.48 & 0.52 & \textcolor{black}{0.009} & \textcolor{black}{0.011} & \textbf{0.04} \\
  \citet{Pyc2010} & Social Sciences & 9.18 & 0.38 & \textcolor{black}{0.011} & \textcolor{black}{0.004} & \textbf{0.061} \\
  \citet{Nichols2006} & Experimental Philosophy & 9.40 & 0.49 & \textcolor{black}{0.015} & \textcolor{black}{0.0006} & \textbf{0.049} \\
   \bottomrule
\end{tabular}%
}
\end{table}
Two studies from the Psychology project show replication success but fail the
two-trials rule. These studies show $p$-values that are slightly above the
significance threshold in either original or replication study, but do not
exhibit much shrinkage; in the replication of \citet{Oberauer2008}, the
replication $p$-value was $p_r = 0.035$, a little too large to pass the
two-trials rule. However, as the replication effect estimate shrunk only about
$30$\% compared to the original one, replication success is still achieved.
Conversely, the original $p$-value $p_o = 0.028$ in \citet{Schmidt2008} was just
above the significance level, yet the replication led to a highly significant
result $p_r < 0.0001$ with the effect estimate being even $30$\% larger than the
original counterpart, which therefore also resulted in replication success.

@@

This analysis was based on the default choice $\dinfty=1$ at $\alpha=0.025$ for
the golden level as described in Section \ref{sec1:goldenthresh}. We may also
choose a different value for the limiting relative effect size $\dinfty$ at
$\alpha=0.025$ which then corresponds to $\dinfty=1$ at a different level
$\alpha'$ as given in \eqref{eq1:alphaPrime}. Figure \ref{fig1:fig7} compares the
proportion of successful replications with the replication success approach for
$\dinfty \in (0.5, 1.1)$ with the two-trials rule at the
corresponding levels
$\alpha' \in (0.06, 0.022)$ for
all four replication projects. We can see that the two proportions agree fairly
well for all values of $\alpha'$ considered. The number of discrepant studies in
each project varies between 0 and 3. Only in the Psychology project there are
some studies which are successful with the replication success approach but not
the two-trials rule and some studies successful with the two-trials rule but not
the replication success approach. The proportion of studies where both methods
are successful (also shown in Figure \ref{fig1:fig7}) is then smaller than the
proportion of successful replications with either one of the two methods. The
three discrepant studies from the Psychology project listed in the top three
rows of Table~\ref{tbl:discrep} are an example of this particular feature.

@@

\end{knitrout}
\caption{Proportion of successful replications as a function of the limiting
  relative effect size $\dinfty$ at $\alpha = 0.025$. The upper axis gives the
  equivalent level $\alpha'$ where the corresponding limiting relative effect
  size is 1. The replication success (RS) approach is compared with the
  two-trials rule (2TR).}
\label{fig1:fig7}
\end{figure}

\section{Discussion}\label{sec1:discussion}
In this paper, we have expanded on the replication success approach introduced
in \citet{Held2020} and demonstrated its advantages over alternative methods
such as the two-trials rule. In particular, the method provides an attractive
compromise between hypothesis testing and estimation,
as it penalizes
shrinkage of the replication effect estimate compared to the original one,
while ensuring that both are statistically significant to some extent.
%% For instance, the method will indicate only a low degree of replication success when
%% the replication study shows a much smaller but statistically significant
%% effect estimate, whereas it can still indicate some degree of
%% success when either original or replication $p$-value are slightly above the
%% significance level. %% , provided their effect estimates are compatible.

@@

Throughout the paper we have assumed that the relative sample size is fixed in
advance. In practice the sample size of the replication study is often chosen
based on the result of the original study \citep{Anderson2017}. Power
calculations as shown in Figure \ref{fig1:fig3} can then be inverted to determine
the appropriate sample size of the replication study. We can also invert
equation \eqref{eq1:res} to obtain the required replication sample size based on
the specification of the minimum relative effect size $\dmin$ to achieve
replication success. This novel way of calculating the sample size requires the
specification of the minimum relative effect size which can still be considered
as acceptable. Sample size calculations based on the two-trials rule can also be
formulated in terms of the minimum relative effect size by inverting equation
\eqref{eq1:dSig}. We will report on a detailed comparison of the different
approaches in future work.

### 2022-12-05 thesis.Rnw
change paper order 1 and 2
table formatting

<< "main-setup", include = FALSE, echo = FALSE, warning = FALSE, message = FALSE >>=
## knitr options
library(knitr)
opts_chunk$set(fig.height = 4,
               echo = FALSE,
               warning = FALSE,
               message = FALSE,
               cache = TRUE,
               eval = TRUE)

## should sessionInfo be printed at the end?
Reproducibility <- FALSE

## Packages
library(ggplot2) # plotting
library(xtable) # table
library(ReplicationSuccess) # replication study stuff
library(dplyr) # data manipulation
library(UpSetR) # upset plot

@@

\addtocontents{toc}{\bigskip}

@@

% Paper I
% ------------------------------------------------------------------------------
\paperchapter{%
 The assessment of replication success based on relative effect size
}{%
  Leonhard Held, Charlotte Micheloud, Samuel Pawel
}{%
   \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
  \href{https://doi.org/10.1214/21-AOAS1502}{doi:10.1214/21-AOAS1502}}
\include{paper2}

% Paper II
% ------------------------------------------------------------------------------
\paperchapter{%
 The sceptical Bayes factor for the assessment of replication success
}{%
  Samuel Pawel, Leonhard Held
}{%
   \textit{Journal of the Royal Statistical Society: Series B (Statistical Methodology)}, 2022, 84(3), 879--911.
   \href{https://doi.org/10.1111/rssb.12491}{doi:10.1111/rssb.12491}
 }
\include{paper1}

% Paper III
% ------------------------------------------------------------------------------
\paperchapter{%
  Bayesian approaches to designing replication studies}{%
  Samuel Pawel, Guido Consonni, Leonhard Held}{%
  2022. arXiv preprint. \href{https://doi.org/10.48550/arXiv.2211.02552}{doi:10.48550/arXiv.2211.02552}
}
\include{paper3}

\addtocontents{toc}{\bigskip}
\addtocontents{toc}{%
  \protect\vspace{2ex}
  \textbf{\textsf{Reverse-Bayes methodology}}\par}
\addtocontents{toc}{%
  \protect\vspace{-2ex}
  \par\noindent\rule{\textwidth}{0.4pt}\par}

% Paper IV
% ------------------------------------------------------------------------------
\paperchapter{%
 Reverse-Bayes methods for evidence assessment and research synthesis
}{%
  Leonhard Held, Robert Matthews, Manuela Ott, Samuel Pawel
}{%
  \textit{Research Synthesis Methods}, 2022, 13(3), 295--314.
  \href{https://doi.org/10.1002/jrsm.1538}{doi:10.1002/jrsm.1538}
}
\include{paper4}

@@

% Paper V
% ------------------------------------------------------------------------------
\paperchapter{%
 Comment on ``Bayesian additional evidence for decision making under small
sample uncertainty''
}{%
  Samuel Pawel, Leonhard Held, Robert Matthews
}{%
  \textit{BMC Medical Research Methodology}, 2022, 22(149).
  \href{https://doi.org/10.1186/s12874-022-01635-4}{doi:10.1186/s12874-022-01635-4}
}
\include{paper5}

\addtocontents{toc}{\bigskip}
\addtocontents{toc}{%
  \protect\vspace{2ex}
  \textbf{\textsf{Integrity in methodological research}}\par}
\addtocontents{toc}{%
  \protect\vspace{-2ex}
  \par\noindent\rule{\textwidth}{0.4pt}\par}

% Paper VI
% ------------------------------------------------------------------------------
\paperchapter{%
  Pitfalls and Potentials in Simulation Studies }{%
  Samuel Pawel, Lucas Kook, Kelly Reeve }{%
  2022. arXiv preprint.
  \href{https://doi.org/10.48550/arXiv.2203.13076}{doi:10.48550/arXiv.2203.13076}
}

>>>>

<< "main-setup", include = FALSE, echo = FALSE, warning = FALSE, message = FALSE >>=
## knitr options
library(knitr)
opts_chunk$set(fig.height = 4,
               echo = FALSE,
               warning = FALSE,
               message = FALSE,
               cache = FALSE,
               eval = TRUE)

## should sessionInfo be printed at the end?
Reproducibility <- TRUE

## Packages
library(ggplot2) # plotting
library(ggpubr) # combining ggplots
library(scales) # scales for plots
library(xtable) # table
library(ReplicationSuccess) # replication study stuff
library(dplyr) # data manipulation
library(UpSetR) # upset plot

@@

\addtocontents{toc}{\bigskip}
\addtocontents{toc}{\bigskip}

@@

% Paper I
% ------------------------------------------------------------------------------
\paperchapter{%
 The assessment of replication success based on relative effect size
}{%
  Leonhard Held, Charlotte Micheloud, Samuel Pawel
}{%
   \textit{The Annals of Applied Statistics}, 2022, 16(2), 706--720.
  doi:\href{https://doi.org/10.1214/21-AOAS1502}{10.1214/21-AOAS1502}}
\include{paper1}

% Paper II
% ------------------------------------------------------------------------------
\paperchapter{%
 The sceptical Bayes factor for the assessment of replication success
}{%
  Samuel Pawel, Leonhard Held
}{%
   \textit{Journal of the Royal Statistical Society: Series B (Statistical Methodology)}, 2022, 84(3), 879--911.
   doi:\href{https://doi.org/10.1111/rssb.12491}{10.1111/rssb.12491}
 }
\include{paper2}

% Paper III
% ------------------------------------------------------------------------------
\paperchapter{%
  Bayesian approaches to designing replication studies}{%
  Samuel Pawel, Guido Consonni, Leonhard Held}{%
  2022. arXiv preprint. doi:\href{https://doi.org/10.48550/arXiv.2211.02552}{10.48550/arXiv.2211.02552}
}
\include{paper3}

\addtocontents{toc}{\bigskip}
\addtocontents{toc}{\bigskip}
\addtocontents{toc}{%
  \protect\vspace{2ex}
  \textbf{\textsf{Reverse-Bayes methodology}}\par}
\addtocontents{toc}{%
  \protect\vspace{-2ex}
  \par\noindent\rule{\textwidth}{0.4pt}\par}

% Paper IV
% ------------------------------------------------------------------------------
\paperchapter{%
 Reverse-Bayes methods for evidence assessment and research synthesis
}{%
  Leonhard Held, Robert Matthews, Manuela Ott, Samuel Pawel
}{%
  \textit{Research Synthesis Methods}, 2022, 13(3), 295--314.
  doi:\href{https://doi.org/10.1002/jrsm.1538}{10.1002/jrsm.1538}
}
\include{paper4}

@@

% Paper V
% ------------------------------------------------------------------------------
\paperchapter{%
 Comment on ``Bayesian additional evidence for decision making under small
sample uncertainty''
}{%
  Samuel Pawel, Leonhard Held, Robert Matthews
}{%
  \textit{BMC Medical Research Methodology}, 2022, 22(149).
  doi:\href{https://doi.org/10.1186/s12874-022-01635-4}{10.1186/s12874-022-01635-4}
}
\include{paper5}

\addtocontents{toc}{\bigskip}
\addtocontents{toc}{\bigskip}
\addtocontents{toc}{%
  \protect\vspace{2ex}
  \textbf{\textsf{Integrity in methodological research}}\par}
\addtocontents{toc}{%
  \protect\vspace{-2ex}
  \par\noindent\rule{\textwidth}{0.4pt}\par}

% Paper VI
% ------------------------------------------------------------------------------
\paperchapter{%
  Pitfalls and Potentials in Simulation Studies }{%
  Samuel Pawel, Lucas Kook, Kelly Reeve }{%
  2022. arXiv preprint.
  doi:\href{https://doi.org/10.48550/arXiv.2203.13076}{10.48550/arXiv.2203.13076}
}
